Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
motivate batch processing API further
@glouppe: I snuck the online learning algos back in so as not to give
the false impression that we're tied to batch learning algorithms.
The remark is shorter now.

The public API is oriented towards batch processing rather than online
processing. While classification and regression algorithms can indeed make
predictions for single samples, most \sklearn objects are however intended to be
used on batches of data. For efficiency reasons, this makes the use of NumPy and
SciPy optimal by preventing the overhead inherent to Python function calls or
due to per-element dynamic type checking.
% Gilles: I don't think it is worth elaborating too much (if at all) on online learning. They are exceptions in scikit-learn.

% The public API is oriented toward batch processing
% to enable efficient implementation.
% While classification and regression algorithms
% can make predictions for single samples,
% and some algorithms in \sklearn can perform online learning
% (e.g. stochastic gradient descent for linear SVMs and logistic regression,
% an online variant of $k$-means based on \citealt{sculley2010web}),
% these algorithm are really intended to be used on small batches of samples.
% Doing so makes optimal use of NumPy and SciPy
% because they prevent the overhead inherent in Python function calls
% and the language's per-element dynamic type checking.

>>>>

The public API is oriented towards batch processing
rather than processing single samples per API call.
While classification and regression algorithms can indeed make predictions
for single samples,
\sklearn objects are not optimized for this use case.
(The few online learning algorithms implemented
are intended to take minibatches.)
Batch processing makes optimal use of NumPy and SciPy
by preventing the overhead inherent to Python function calls
and per-element dynamic type checking.
Although this might seem to be an artifact of the Python language,
and therefore an implementation detail that leaks into the API,
we argue that APIs should be designed
so as to not tie a library to a suboptimal implementation strategy,
and batch processing can enable fast implementations
in lower-level languages as well
(where locality of reference effects
and the possibility of internal parallelization come into play).
% Gilles: I don't think it is worth elaborating too much (if at all) on online learning. They are exceptions in scikit-learn.
